Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-18 EconGrowth.Rnw
Added author and contact information to the frontmatter of the article.
Now using 4 digits after the decimal in tables.

\title{}

@@

\author{}

\address{}

\begin{abstract}
%% Text of abstract

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

@@

# Combine all estimates and their confidence intervals into data frames with intelligent row names
estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = NA)
row.names(estCD) <- "Cobb-Douglas"
#row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
 # The [1] subscripts pick off the lower confidence interval
lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
row.names(lowerCD) <- "- 95% CI"
 # The [2] subscripts pick off the lower confidence interval
upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
row.names(upperCD) <- "+ 95% CI"

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD  <- xtable(dataCD)
@

<<CD Results, results='asis'>>=
print(xtable(dataCD), floating=FALSE)
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, sanitize.text.function = function(x){x})
@

@@

# Now create the data for a table.
dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCDq <- xtable(dataCDq)

dataAll <- rbind(dataCD, dataCDq); dataAll
@

<<CDq Results, results='asis'>>=
print(xtable(dataCDq), floating=FALSE)
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDq, sanitize.text.function = function(x){x})

print(xtable(dataAll, floating=FALSE))
@

>>>>

\title{Empirical Analysis of the Role of Energy in Economic Growth}

@@

\author[Calvin]{Caleb Reese}
\author[Calvin]{Lucas Timmer}
\author[Calvin]{Matthew Kuperus Heun \corref{cor1}}
\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}

\cortext[cor1]{Corresponding author}
\address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}

\begin{abstract}
%% Text of abstract
*********** Add abstract ***********
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
economic growth \sep energy \sep cobb-douglas \sep CES \sep LINEX
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

@@

# Combine all estimates and their confidence intervals into data frames with intelligent row names
estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
row.names(estCD) <- "Cobb-Douglas"
#row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
 # The [1] subscripts pick off the lower confidence interval
lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
row.names(lowerCD) <- "- 95% CI"
 # The [2] subscripts pick off the lower confidence interval
upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
row.names(upperCD) <- "+ 95% CI"

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4))
@

<<CD Results, results='asis'>>=
print(tableCD, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, sanitize.text.function = function(x){x})
@

@@

# Now create the data for a table.
dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4))

dataAll <- rbind(estCD, estCDq); dataAll
tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4))
@

<<CDq Results, results='asis'>>=
print(tableCDq, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDq, sanitize.text.function = function(x){x})

print(tableAll, caption.placement="top")
@
